\documentclass{article}
\usepackage[utf8]{inputenc}


\title{A SYSTEMATIC LITERATURE REVIEW ON USING GOOGLE CLOUD PLATFORM IN SOFTWARE DEVEVOLOPMENT. 
}
\author{AKol Sharon Norah}
\date{Mar,10 2018}

\begin{document}

\maketitle

\newpage

\section{Introduction}
\paragraph{Google cloud platform, offered by Google is a suite of cloud computing services that runs on the same infrastructure that Google uses internally for its end-user products such as Google search and You Tube.\cite{myrefone}}





\section{Product Satisfaction}
\paragraph{Why should one google cloud Platform for developing software?}
\paragraph{
Prior research has identified many benefits of using Google cloud platform for software development. This benefits include: Future proof infrastructure; cloud platform is secure, global, high performance, cost effective and constantly improving, Seriously powerful data and analytics; Tap into big data to find answers faster and build better products.  Rather than keeping your most powerful data tools in the hands of a few experts, Google Cloud Platform unlocks data to empower your entire organization, Serverless, just code that is to say grow from prototype to production to planet-scale, without having to think about capacity, reliability or performance. Pay for what you use ?Because of dynamic provisioning and automatic scaling, you pay only for what you use.\cite{myreftwo} }
\paragraph{
In this study and related research, the individuals serving are software developers who are collaborating with google developers. The studied benefits to software developers include programming skills as well as networking opportunities and application of classroom learning to real-world issues. Ultimately, google cloud platform stimulates developers learning and engages developers in their surrounding communities. Google cloud platform creates new goals for developers such as personal development, career development, moral development, academic achievement. These types of projects allow developers to utilize material learned in the classroom to improve societal conditions\cite{myrefthree}.}

\section{Conclusion}
\paragraph{
Google Cloud Platform is a development platform worth investing in for developers since it is secure and fully featured for all enterprises, committed to open source and industry leading price performance and therefore they will achieve a lot out of their projects.}

\newpage
\bibliographystyle{IEEEtran}
\bibliography{ref}

\end{document}
